---
title: "Lasso with Tidymodels"
output:
  html_document:
    number_sections: true
    fig_caption: true
    fig_width: 5
    fig_height: 4
    theme: cosmo
    highlight: tango
    code_folding: show
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      fig.align = "center")
```

Let's apply Lasso model to the data.

![Photo by <a href="https://unsplash.com/@sxy_selia?utm_source=unsplash&utm_medium=referral&utm_content=creditCopyText">Sangga Rima Roman Selia</a> on <a href="/s/photos/house-price?utm_source=unsplash&utm_medium=referral&utm_content=creditCopyText">Unsplash</a>
  ](https://images.unsplash.com/photo-1559230928-34c7c281d7c7?ixid=MXwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHw%3D&ixlib=rb-1.2.1&auto=format&fit=crop&w=1263&q=80)

# Preparations (준비작업) {.tabset .tabset-fade}

## Libraries

We mainly exploits the functions from the tidyvers and tidymodels packages. `magrittr` has my favorite operators!

```{r load_lib, message=FALSE, warning=FALSE, results='hide'}
library(tidymodels)
library(tidyverse)
library(magrittr)
library(skimr)
library(knitr)
theme_set(theme_bw())
```

## Data load

```{r}
file_path <- "../input/house-prices-advanced-regression-techniques/"
files <- list.files(file_path)
files
```

```{r, message=FALSE}
train <- read_csv(file.path(file_path, "train.csv"))
test <- read_csv(file.path(file_path, "test.csv"))
```


# Data overview (데이터 기본정보) {.tabset .tabset-fade}

## Basic info.

Here is the basic information about `train` and `test`. We have approximately the same sample size for the train and test set. The number of columns in the train is 81 and the one in the test is 80.

```{r}
dim(train)
dim(test)
```

We can see train doesn't have the target variable `SalePrice`.

```{r}
"SalePrice" %in% names(test)
```


## Detailed info. `train`

```{r}
skim(train)
```

## Detailed info. `test`

```{r}
skim(test)
```

# EDA with visualization (탐색적 데이터 분석) {.tabset .tabset-fade}

## Distribution of `sale_price`

If we check out the distribution of the house price, it is little bit skewed to the right.

```{r message=FALSE, class.source = 'fold-hide'}
train %>% 
  ggplot(aes(x = SalePrice)) +
  geom_histogram()
```
Since we want to build a linear regression assume that the noise follows the normal distribution, let us take a log to `SalePrice` variable.

```{r message=FALSE, class.source = 'fold-hide'}
train %>% 
  ggplot(aes(x = log(SalePrice))) +
  geom_histogram()
```

## `NA`s

There is a nice package for checking out `NA`s. Let's see how many variables we have which contains `NA`s.

```{r message=FALSE, warning=FALSE, class.source = 'fold-hide'}
library(naniar)
train %>% 
  # select_if(~sum(is.na(.)) > 0) %>% # alternative way
  select(where(~sum(is.na(.)) > 0)) %>% 
  gg_miss_var()
```

We can do more analysis about `NA`s with `upset()` function, which shows that most of the observations with `NA`s in the data set have `NA`s at the `PoolQC`, `MiscFeature`, `Alley`, `Fence` at the same time.

```{r message=FALSE, class.source = 'fold-hide'}
train %>% 
  select(where(~sum(is.na(.)) > 0)) %>% 
  gg_miss_upset()
```

From the above, we can have some insights that if a house doesn't have Pool, it is likely that it doesn't have Alley, Fence, and Fireplace too.

# Preprecessing with `recipe` (전처리 레시피 만들기)

First, I would like to clean the variable names with `janitor` package so that we have consistent varible names.

## `all_data` combine and name cleaning with `janitor`

```{r}
all_data <- bind_rows(train, test) %>% 
  janitor::clean_names()
names(all_data)[1:10]
```

## Make recipe

Note that we will use mode imputation for nominal variables for the baseline, and the mean imputation for the numerical variables. However, this should be changed to build a more sensitive model because we have checked that the `NA` in the nominal variables indicates that cases where the house doesn't have the corresponding attributes.

```{r}
housing_recipe <- all_data %>% 
  recipe(sale_price ~ .) %>%
  step_rm(id) %>% 
  step_log(sale_price) %>% 
  step_modeimpute(all_nominal()) %>% 
  step_dummy(all_nominal()) %>% 
  step_meanimpute(all_predictors()) %>%
  step_normalize(all_predictors()) %>% 
  prep(training = all_data)

print(housing_recipe)
```

## `juice` the all_data2 and split

```{r}
all_data2 <- juice(housing_recipe)
```

We are done for preprocessing. Let's split the data set.

```{r}
train_index <- seq_len(nrow(train))
train2 <- all_data2[train_index,]
test2 <- all_data2[-train_index,]
```


```{r}
train2 %>% 
  head() %>% 
  kable()
```

# Set Ridge regression model and fitting (Ridge regeression 모델 설정 및 학습)

Set `mixture` is equal to zero refering the Ridge regression in `glmnet` since the 

```{r message=FALSE, warning=FALSE}
lasso_model <- 
    linear_reg(penalty = 0.01, mixture = 1) %>% # lasso: 1, ridge: 0
    set_engine("glmnet")

lasso_fit <- 
    lasso_model %>% 
    fit(sale_price ~ ., data = train2)

options(max.print = 10)
lasso_fit %>% 
    tidy() %>% 
    filter(estimate > 0.001)
```

# Prediction and submit (예측 및 평가)

```{r warning=FALSE}
result <- predict(lasso_fit, test2)
result %>% head()
```

```{r}
submission <- read_csv(file.path(file_path, "sample_submission.csv"))
submission$SalePrice <- exp(result$.pred)
write.csv(submission, row.names = FALSE,
          "lasso_regression_0point1.csv")
```



