---
title: "Get your boat tidy"
output:
  html_document:
    number_sections: true
    fig_caption: true
    toc: true
    fig_width: 5
    fig_height: 4
    theme: cosmo
    highlight: tango
    code_folding: show
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      message = FALSE,
                      warning = FALSE,
                      fig.align = "center")
```


![Photo stealed from [here](https://unsplash.com/photos/Yi_S3JgxMmk)](https://images.unsplash.com/photo-1572969065830-5c390f345b78?ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&ixlib=rb-1.2.1&auto=format&fit=crop&w=1891&q=80)

# Preperation {.tabset .tabset-fade}

## Library load

Load R pacakges for Kaggling. I usually use these for any notebook thesedays, why not in here? 🤣

```{r load_lib, message=FALSE, warning=FALSE, results='hide'}
# remotes::install_github("curso-r/treesnip")
library(treesnip)
library(tidymodels)
library(tidyverse)
library(magrittr)
library(skimr)
library(knitr)
theme_set(theme_bw())
```

## Dataset load

These are the file list in the competition. We have only `train` and `test` data for this notebook.

```{r}
file_path <- "../input/tabular-playground-series-apr-2021/"
files <- list.files(file_path)
files
```

One note; I love to convert the variables names by using `janitor` package because the result are consist and not distracting.

```{r, message=FALSE}
train <- read_csv(file.path(file_path, "train.csv")) %>% 
  janitor::clean_names()
test <- read_csv(file.path(file_path, "test.csv")) %>% 
  janitor::clean_names()
```

# Basic info. {.tabset .tabset-fade}

## Basic info.

This competition data set has very simple structure. `train` has 100,000 samples and `train` has 100,000 samples.

```{r}
dim(train)
dim(test)
```

The list of the variables in `train` we have is as follows:

```{r class.source = 'fold-hide'}
index <- 1:ncol(train)
glue::glue("Train set variable {index}: {names(train)}") 
```

The list of the variables in `test` we have is as follows:

```{r class.source = 'fold-hide'}
index <- 1:ncol(test)
glue::glue("Train set variable {index}: {names(test)}") 
```

As we can see the `test` data doesn't have the `survived` variable; which is the target variable we need to predict!

## train and test data snippet

```{r}
head(train) %>% kable()
head(train) %>% kable()
```

## train data skim

`skim()` function is useful for you to get the big picture about your data. It generates the tidy report of your data set. 

```{r}
skim(train)
```

When we look at the complete rate for each variables, `cabin` have a most missing values.

## test data skim

Test data also has a similar distribution of missing values, too. However, one thing that I have notice here is that `age` in test data set has a slightly different distribution than the one of `train` data set.

```{r}
skim(test)
```

# Simple visualization {.tabset .tabset-fade}

Here are some visualization code, you can adjust this little bit for your own EDA. The following is the distribution of our target variable; as we can see this is a balanced data set. 😆

```{r message=FALSE, class.source = 'fold-hide'}
train %>% 
    count(survived) %>% 
    mutate(proportion = n / sum(n)) %>% 
    ggplot(aes(x = factor(survived), y = proportion, 
               fill = factor(survived))) +
    geom_bar(stat = "identity") +
    labs(title = "Bar chart for target variable",
         subtitle = "Variable label: 'survived'",
         x = "Survived") +
    scale_fill_brewer(palette = "Set1",
                      labels = c("No", "Yes")) +
    guides(fill = guide_legend(title = "Survival",
                               ncol = 2, )) +
    theme(legend.position = "bottom")
```

# Preprocessing with `recipe`

## `all_data` combine

Before I combine the `train` and `test` set, I transformed `weekly_sale`, and then combined them into `all_data`.

```{r}
all_data <- bind_rows(train, test)
all_data %>% head()
names(all_data)
dim(all_data)
```

## Make preprocessing recipe

`recipe` has useful step [functions](https://recipes.tidymodels.org/reference/index.html) for data preprocessing. This will save your a lot of time!

```{r}
titanic_recipe <- all_data %>% 
    recipe(survived ~ .) %>%
    step_mutate(
        survived = factor(survived),
        last_name = word(name, 1)
        ) %>% 
    step_modeimpute(embarked) %>% 
    step_meanimpute(age, fare) %>% 
    step_rm(passenger_id, cabin, ticket) %>% 
    step_integer(all_nominal(), -all_outcomes()) %>% 
    step_center(all_predictors(), -all_outcomes()) %>% 
    prep(training = all_data)

all_data2 <- juice(titanic_recipe)
all_data2 %>% dim()
all_data2 %>% head()
```

`juice()` function will give you the actual preprocessed data.

# Calculate model

## Split the data set

Let's split the data again since we are done for the preprocessing.

```{r}
train_index <- seq_len(nrow(train))
train2 <- all_data2[train_index,]
test2 <- all_data2[-train_index,]
```

## Validation split

```{r}
set.seed(2021)

# 10 fold cv
validation_split <- vfold_cv(v = 5, train2, strata = survived)
```

## LightGBM specification

```{r}
# Main Arguments:
#   mtry = 1
#   trees = 10000
#   min_n = 38
#   tree_depth = 10
#   learn_rate = 0.005
#   loss_reduction = 0.0672681981394635
#   sample_size = 0.45471338326586
#   stop_iter = 10

lightgbm_spec <- boost_tree(
    trees = 10000, 
    tree_depth = 100, 
    mtry = tune(),
    min_n = tune(), 
    loss_reduction = 0.0672681981394635,  
    sample_size = 0.45471338326586, 
    learn_rate = 0.005,
    stop_iter = 10,
) %>% 
    set_engine('lightgbm',
               num_leaves = 60,
               # categorical_feature = c(1, 2, 5, 6, 8, 10),
               num_threads = 10) %>% 
    set_mode('classification')

lightgbm_spec %>% translate()

param_grid <- grid_random(
    finalize(mtry(), train2[-1]),
    min_n(), 
    # loss_reduction(),
    # sample_size = sample_prop(range = c(0.4, 1)),
    size = 15
) %>% filter(mtry > 3)
param_grid
```

# Workflow

```{r}
lightgbm_workflow <- workflow() %>%
    add_model(lightgbm_spec) %>% 
    add_formula(survived ~ .)
```

# Tunning

```{r}
library(tictoc)
tic()
tune_result <- lightgbm_workflow %>% 
  tune_grid(validation_split,
            grid = param_grid,
            metrics = metric_set(accuracy))
toc()
```
## Tunning result

```{r}
tune_result$.notes[[1]]$.notes
tune_result %>% 
    collect_metrics()
```

```{r}
tune_result %>% show_best()
```


```{r}
tune_best <- tune_result %>% select_best(metric = "accuracy")
final_spec <- finalize_model(lightgbm_spec, tune_best)
final_spec
# Boosted Tree Model Specification (classification)
# 
# Main Arguments:
#   mtry = 1
#   trees = 10000
#   min_n = 38
#   tree_depth = 10
#   learn_rate = 0.005
#   loss_reduction = 0.0672681981394635
#   sample_size = 0.45471338326586
#   stop_iter = 10
# 
# Engine-Specific Arguments:
#   num_leaves = 60
#   num_threads = 10
# 
# Computational engine: lightgbm 
```

## Fitting the model

```{r}
lightgbm_workflow %<>% update_model(final_spec)
lightgbm_fit <- fit(lightgbm_workflow, data = train2)
```

# Prediction

```{r}
result <- predict(lightgbm_fit, test2)
result %>% head()
```


# Submission

```{r}
submission <- read_csv(file.path(file_path, "sample_submission.csv"),
                       col_types = cols(PassengerId = col_integer(),
                                        Survived = col_integer()))
submission$Survived <- result$.pred_class %>% as.integer() - 1
write.csv(submission, row.names = FALSE,
          "lightgbm_baseline.csv")
submission %>% head()

# write.csv(result2, row.names = FALSE,
#           "group_mean.csv")
```
